**The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models**

### 2021-03-08 Manuscripts/Manuscript_AM_v3.Rmd
NEed to improve labels

#original bases
p1<-ggplot(basis_plot,aes(x=time,y=value_orig,colour=factor(Basis)))+
  geom_line()+geom_point()+
  facet_grid(~Basis)+
  theme_classic()+
  scale_color_aaas()

#basis multiplied by the coefficient
p2<-ggplot(basis_plot,aes(x=time,y=mod_val,colour=factor(Basis)))+
  geom_line()+geom_point()+
  facet_grid(~Basis)+
  theme_classic()+
  scale_color_aaas()

#heatmap of the coefficient
p3<-ggplot(basis_plot,aes(x=Basis,y=Basis,fill=cof))+
  geom_tile(aes(color='black'),size=2)+
  geom_tile(size=2)+
  scale_fill_gradient(low = "white", high = "red")+ 
  geom_text(aes(label=round(cof,1)))+
  theme_classic()

@@

p1+p2+p3+p4+plot_annotation(tag_levels='A')
#plotting
#plot(dat$y~dat$time)

>>>>

#original bases
p1<-ggplot(basis_plot,aes(x=time,y=value_orig,colour=as.factor(Basis)))+
  geom_line()+geom_point()+
  labs(y='Original basis function',fill="Basis Number")+
  facet_grid(~Basis)+
  theme_classic()+
  scale_color_aaas()

#basis multiplied by the coefficient
p2<-ggplot(basis_plot,aes(x=time,y=mod_val,colour=as.factor(Basis)))+
  geom_line(show.legend = FALSE)+geom_point(show.legend = FALSE)+
  labs(y='Modified basis function')+
  facet_grid(~Basis)+
  theme_classic()+
  scale_color_aaas()

#heatmap of the coefficient
p3<-ggplot(basis_plot,aes(x=Basis,y=Basis,fill=cof))+
  geom_tile(aes(color='black'),size=2,show.legend = FALSE)+
  geom_tile(size=2)+
  scale_fill_gradient(low = "white", high = "red")+ 
  geom_text(aes(label=round(cof,1)))+
  theme_classic()

@@

p1+p3+p2+p4+plot_annotation(tag_levels='A')
#plotting
#plot(dat$y~dat$time)
